---
title: "Visualization of US airport delay in May 2017"
author: "Zeping He"
subtitle: 
output:
    html_document:
        code_folding: show
---


# Introduction
 **Problem Statement**

* Many major airports around the US have significant delay problems as a result of increasing demand of passenger. The world aviation industry has a significant growth in the quantity of the travelers. In the year of 2016, 3.8 billion air travelers fly all over the earth. The International Air Transport Association (IATA) expects 7.2 billion passengers to travel in 2035, a near doubling of air travelers in 2016.
*In the United States, average arrival delays at 85 airports were greater than 15 minutes in 2017, 836,017 were effected and only 78.80% of all schedule flights is on time.

 **Objective**
 
* Deliver the airport delay distribution information in US from visual approach.
* Test if the schedulle flights in each airport are evenly affect by the average delay-time. 
* Test the correlation between passengers traffic and delay time.

 **Importance**
 
* Make a better understanding of airport departure delay in US
* Lead a further research in filght path.


<br>
<br>

<hr color="#000000">

# Materials and methods {.tabset}

<br>

## Packages
```{r, message=FALSE, result=FALSE, warning=FALSE, tidy=TRUE}
library(dplyr)
library(ggplot2)
library(maps)
library(spocc)
library(leaflet)
library(rbokeh)
library(widgetframe)
library(ggpubr)
library(stats)
library(geosphere)
library(readr)
library(DT)
library(highcharter)
knitr::opts_chunk$set(cache=TRUE)  # cache the results for quick compiling
```


<br>
<br>

<hr color="#000000">

##Data Source
**Click the hyperlink to select which variables of the data from BTS Website you want use.**


* <a href="https://www.transtats.bts.gov/Tables.asp?DB_ID=120&DB_Name=Airline%20On-Time%20Performance%20Data&DB_Short_Name=On-Time"> Filght on-time Performance </a> --- 'Airline On-Time Performance Data'  From BUREAU OF TRANSPORTATION STATISTICS
* <a href= "https://www.transtats.bts.gov/Tables.asp?DB_ID=595&DB_Name=Aviation%20Support%20Tables"> Airport Location Data </a> --- 'Aviation Support Tables'  BUREAU OF TRANSPORTATION STATISTICS


To save time, I already have three tables prepared. 
```{r, message=F, warning=F}

May17flight <- read_csv("https://raw.githubusercontent.com/finallyegg/RDataScience_Project/master/data/May17flight.csv")

AirportData <- read_csv("https://raw.githubusercontent.com/finallyegg/RDataScience_Project/master/data/AirportData.csv")

Halfflow <- read_csv("https://raw.githubusercontent.com/finallyegg/RDataScience_Project/master/data/Halfflow.csv")


```


<br>
<br>

<hr color="#000000">

## Data Processing and Methodology
Because of the airline on-time data was described by the departure delay and arrival delay. Each flight can be considered as two spatial point -- Departure airport and Arrival airport. To study the punctuality rate of each flight, focusing on departure airport on time rate is important. 

 **0.Check if the data have duplicated**

```{r, message=F, warning=F}
length(AirportData$Code[duplicated(AirportData$Code)])
```

The result said there are 1449 Airport which have the same 'Code' but different detailed named. But the location is the same. 

Remove duplicated Data in AirportData_table
```{r, message=F, warning=F}
AirportData_nd=AirportData[!duplicated(AirportData$Code),]
```

 **0.5 Georeference each airport by using "left-join" function.**
 
 Assign each Origin Airport a coordinate base on their 3-digit 'Code', Left-join  is based on the same string (names) of two tables. 

```{r, message=F, warning=F}
codeunique=data.frame(unique(May17flight$ORIGIN))
colnames(codeunique)="Code"
airport_joined=left_join(codeunique, AirportData_nd, by = "Code")

```

 **1.Extract and aggregate the origin and destination location from the flight database **

Since we have each flight origin and destination, we can group these flight by their origin location. By using <code>'group by'</code> or <code>'aggregate'</code> function, to group data by certain variable(s).

In this case, I am using 'mean' function to obtain the airport average delay value, so each seperate flight data will be classified and transformed as the airport data.


Then perform left-join serval times to generate a 'final' table contains 'Airport Code', 'Delay Time', 'Passengers Flow' and 'coordinate'

```{r, warning=F,message=F}
#In this case, I use 'aggregate' to extract the 12th and 13th column from May17flight data table, these columns contains the departure and arrival delay time for each flight. 
monthlydata=aggregate(May17flight[, 12:13], list(May17flight$ORIGIN), mean,na.rm=T)
#Rename the column from 'Group.1' to 'Code' to make it easier to merage in next steps
colnames(monthlydata)[colnames(monthlydata)=="Group.1"]="Code"
#add geographical coordinates information to each airport
l2=left_join(monthlydata, AirportData_nd, by = "Code")
#add passengers traffic information
finished=left_join(l2, Halfflow, by = c("Code" = "ORIGIN"))
```

<br>


 **2.Using leaflet Visualizing the  Airport average delay time **

Leaflet is one of the most popular open-source JavaScript libraries for interactive maps. It’s used by websites ranging from The New York Times and The Washington Post to GitHub and Flickr, as well as GIS specialists like OpenStreetMap, Mapbox, and CartoDB. This R package makes it easy to integrate and control Leaflet maps in R.

<br>

a. Distribution of US public airport
   To generate a basic knowledge of the airport spatial distribution, I made a point map to show the distribution. 

```{r, warning=F,message=F}
m1=leaflet(airport_joined,options = leafletOptions(minZoom = 3, maxZoom = 5)) %>% 
  #set the center point and scale level (3)
   setView(-96, 37.8, 3) %>% 
  #add provider base map
   addProviderTiles(providers$CartoDB.DarkMatterNoLabels) %>%  
   addCircleMarkers(lng=~LONGITUDE,lat=~LATITUDE,
  #this label commands creates a hover 
   label=airport_joined$DISPLAY_AIRPORT_NAME,
   radius = 2,
   stroke = F,
   fillColor = "Orange",
   fillOpacity = 1) %>% 
   frameWidget(width = "100%",height = 500)
```

<br>

b. Create a color ramp based on given interval and certatin domain.
   In this case, interval is set every 15 minutes

```{r, warning=F,message=F}
#set the interval every 15minutes
colbm2=c(0,15,30,45,60,Inf)
#set the color ramp based on the given interval and use delay time as a domin
pal <- colorBin("YlOrRd", domain = finished$DEP_DELAY_NEW,bins = colbm2)

```

<br>

c. Create a circle point map of airport, assign a color ramp for the linear delay percentage. The radius of the 
   circle represents the numberic of passenger traffic in that airport. 


```{r, warning=F,message=F}
popuplabels <- paste(finished$DISPLAY_AIRPORT_NAME,"Airport",
                 "<br>Average Delay Here is</br>",round(finished$DEP_DELAY_NEW),"minutes","<br>Passenger Traffic Here is</br>",finished$Flow)



m2=leaflet(finished,options = leafletOptions(minZoom = 4, maxZoom = 6)) %>% 
  setView(-96, 37.8, 4) %>% 
  addProviderTiles(providers$CartoDB.DarkMatter) %>%
  #add markers and customize the properities
  addCircleMarkers(
    stroke = FALSE,
    color=~pal(finished$DEP_DELAY_NEW),
    popup = popuplabels,
    radius = ~sqrt(finished$Flow)*0.01,
    fillColor =~pal(finished$DEP_DELAY_NEW),
    fillOpacity = 0.7, opacity = 0.7 ) %>% 
  #set Legend properities
  addLegend(
    pal = pal, 
    values = ~DEP_DELAY_NEW, 
    opacity = 0.7, 
    title = "Avg.Delaytime <br>in (minutes)</br>",
    position = "bottomleft") %>% 
  setView(-96, 37.8, 4) %>% 
  frameWidget(width = "100%",height = 500)

```

d.Delay which exceed 15 minutes

```{r, warning=F}
a=filter(finished,finished$DEP_DELAY_NEW>15)
colbm3=c(15,30,45,60,Inf)
pal2=colorBin(c("#fed976","#fd8d3c","#fc4e2a","#b10026"), finished$DEP_DELAY_NEW, bins=colbm3)
```



```{r, warning=F}
popuplabels2 <- paste(a$DISPLAY_AIRPORT_NAME,"Airport",
                 "<br>Average Delay Here is</br>",round(a$DEP_DELAY_NEW),"minutes","<br>Passenger Traffic Here is</br>",a$Flow)

m3=leaflet(a) %>% 
    addProviderTiles(providers$CartoDB.DarkMatter) %>% 
    addCircleMarkers(
      lng=a$LONGITUDE, lat=a$LATITUDE,
      color=~pal2(a$DEP_DELAY_NEW),
      popup = popuplabels2,
      radius = ~sqrt(a$Flow)*0.01,
      fillColor =~pal2(a$DEP_DELAY_NEW),
      fillOpacity = 0.7, 
      opacity = 0.7,
      stroke = FALSE) %>% 
    addLegend(
      pal = pal2, 
      values = ~DEP_DELAY_NEW, 
      opacity = 0.7, 
      title = "Avg.Delaytime <br>in (minutes)</br>",
      position = "bottomleft") %>% 
  setView(-96, 37.8, 4) %>% 
  frameWidget(width = "100%",height = 500)

``` 

<br>

e.Delay which exceed 30 minutes

```{r, warning=F}
a1=filter(finished,finished$DEP_DELAY_NEW>30)
colbm4=c(30,45,60,Inf)
pal3=colorBin(c("#fd8d3c","#fc4e2a","#b10026"), a1$DEP_DELAY_NEW, bins=colbm4)
```



```{r, warning=F}
popuplabels3 <- paste(a$DISPLAY_AIRPORT_NAME,"Airport",
                 "<br>Average Delay Here is</br>",round(a$DEP_DELAY_NEW),"minutes","<br>Passenger Traffic Here is</br>",a1$Flow)

m4=leaflet(a1) %>% 
    addProviderTiles(providers$CartoDB.DarkMatter) %>% 
    addCircleMarkers(
      lng=a1$LONGITUDE, lat=a1$LATITUDE,
      color=~pal2(a1$DEP_DELAY_NEW),
      popup = popuplabels2,
      radius = ~sqrt(a1$Flow)*0.01,
      fillColor =~pal3(a1$DEP_DELAY_NEW),
      fillOpacity = 0.7, 
      opacity = 0.7,
      stroke = FALSE) %>% 
    addLegend(
      pal = pal3, 
      values = ~DEP_DELAY_NEW, 
      opacity = 0.7, 
      title = "Avg.Delaytime <br>in (minutes)</br>",
      position = "bottomleft") %>% 
  setView(-96, 37.8, 4) %>% 
  frameWidget(width = "100%",height = 500)

``` 

<br>

 **Adding Curved Flight path using R's graphic Package**
 
 a.Since we finish visualize the departure delay analysis. Next step is visualize flight path from a airport.
   This database contain start point and end point, simplized thousands flight records into one point to point line by taking the median
```{r, warning=F,message=F}
linedf=May17flight %>%
       group_by(ORIGIN,DEST) %>% 
       summarise(dep_delay_ = mean(DEP_DELAY_NEW,na.rm = T),distance = median(DISTANCE,na.rm = T)) %>% 
       left_join(AirportData_nd,by = c("ORIGIN" = "Code")) %>% 
       left_join(AirportData_nd,by = c("DEST" = "Code"))
```

 **Plot Relationship between Passenger flow and Punctuality rate**
 After visualization the average delay of each airport, I want to study the relationship between Punctuality and passenger traffic. Punctuality rate is different from average delay time, because this time we don't need to classify value by mean. Instead, we only need to know the ratio between 'flights departure delay less than 15 minutes' and the total scheduled flight for each airport.

<br>

a.Data Processing

Create a table that contain the on_time_rate info
```{r, warning=F,message=F}
g2=May17flight %>%
    group_by(ORIGIN) %>%
    # add a column named 'On_time_Rate' to have the rate. 
    summarise(On_time_Rate =   
    length(DEP_DELAY_NEW[DEP_DELAY_NEW<=15])/length(DEP_DELAY_NEW))

#Only view the top 50 busiest airport's data
g2a=left_join(g2,Halfflow,by = "ORIGIN")
g2a50=head(arrange(g2a,desc(Flow)), n = 50)
#ggplot(g2a,aes(x = perDelay, y = Flow)) +geom_point() + labs(x="Punctuality rate",y="Passenger flow")
```

<br>
<br>

<hr color="#000000">

# Results

<br>

## Relationship between Passenger flow and Punctuality rate {.tabset}

### Overview of all airports'

```{r, warning=F,message=F}
figure() %>% ly_points(Flow,On_time_Rate,data=g2a, hover=Description,color =g2a$On_time_Rate ) %>% 
  ly_abline(v=mean(g2a$Flow), color = "red",  width =1, alpha=.7) %>% 
  ly_abline(h=mean(g2a$On_time_Rate), color = "red",  width =1, alpha=.7,legend ="Average")

```

<br>
<br>


### Zoom in to the top 50 busiest Airport

```{r, warning=F,message=F}
figure() %>% ly_points(Flow,On_time_Rate,data=g2a50,hover=list(Description,Flow,On_time_Rate),color = On_time_Rate,alpha = 1)%>% 
  ly_abline(v=mean(g2a50$Flow), color = "red",  width =1, alpha=.7) %>% 
  ly_abline(h=mean(g2a50$On_time_Rate), color = "red",  width =1, alpha=.7, legend ="Average")
```

<br>
<br>

### Treemap

```{r, warning=F,message=F}
h1=hchart(g2a50, "treemap", hcaes(x = g2a50$ORIGIN, value = g2a50$Flow, color = g2a50$On_time_Rate)) %>% hc_tooltip(pointFormat = "<b>{point.name}</b>:<br>
             Flow: {point.value:,.0f}<br>
             ") %>% 
  frameWidget(width = "100%",height = 500)
h1
```

<br>
<br>

### Test the Pearson corrleation 
```{r, warning=F,message=F}
cor(g2a$Flow, g2a$On_time_Rate ,  method = "pearson", use = "complete.obs")

##The corrleation shows the relationship between two variables, from -1 to 1. Bigger abs value is, more clear the relation.

ggscatter(g2a50, y = "On_time_Rate", x = "Flow", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          ylab = "On_time_Rate", xlab = "Passenger Flow")
```

<br>
<br>

##Briefly view the distribution of the public airport

View the Location Map Use "Leaflet"
```{r, warning=F,message=F}
m1
```

So how many points in total? 
Check the quantity of Airport in the databese 

```{r, warning=F}
#'length' gives the length of a vector
#'unique' extract the unduplicated string from the selected column
length(unique(May17flight$ORIGIN))
```
So there are 296 airports in the data bases

<BR>
<BR>

##Interactive map of average departure delay for each airport {.tabset}

### Overall view
Click on the point to view the avg.delay time.

The radius of each circle represent the half-year numberic Passenger traffic of each airport.
```{r, warning=F,message=F}
##The radius of each circle represent the half-year numberic passenger traffic of each airport.
#radius = ~sqrt(finished$Flow)*0.01
m2
```

<BR>
<BR>

### Exceed 15mins of delay
Click on the point to view the avg.delay time.

The radius of each circle represent the half-year numberic Passenger traffic of each airport.
```{r, warning=F,message=F}
##The radius of each circle represent the half-year numberic passenger traffic of each airport.
#radius = ~sqrt(finished$Flow)*0.01
m3
```

<BR>
<BR>

### Exceed 30mins of delay
Click on the point to view the avg.delay time.
S
The radius of each circle represent the half-year numberic passenger traffic of each airport.
```{r, warning=F,message=F}
##The radius of each circle represent the half-year numberic passenger traffic of each airport.
#radius = ~sqrt(finished$Flow)*0.01
m4
```

<BR>
<BR>

## Flight network visualization 

we will use <code>gcIntermediate()</code> to generate the coordinates of the shortest arc that connects its start and end point (think distance on the surface of a sphere). After that, we will plot each arc over the map using <code>lines()</code>.

### 8 busiest Airport Flight path {.tabset} 

**In these flight path map, we could see the delay time of each flight is not even distribution. The delay time distribution is more affected by spatial distribution. **

#### JFK
```{r, warning=F,message=F}
JFK1=linedf %>% 
  filter(ORIGIN=="JFK")
```

```{r, warning=F,message=F}
colbm=c(0,15,20,25,30)
col.1 <- adjustcolor("orange red", alpha=0.4)
col.2 <- adjustcolor("blue", alpha=0.9)
edge.pal <- colorRampPalette(c(col.1, col.2), alpha = TRUE)
edge.col <- edge.pal(50)

map("state", fill=T, col="grey8", bg="grey15")

for (i in (1:dim(JFK1)[1])) { 
  inter=gcIntermediate(c(JFK1$LONGITUDE.x[1], JFK1$LATITUDE.x[1]), c(JFK1$LONGITUDE.y[i], JFK1$LATITUDE.y[i]), n=100)
  edge.ind <-(JFK1[i,]$dep_delay_)
  range(edge.ind)
  lines(inter, lwd=edge.ind/30, col=edge.col[edge.ind])
  legend("bottomleft", # position
  legend = colbm, 
  title = "Delayed length",
  fill = edge.pal(5),
  cex = 0.56,
  bty = "n") # border
}
```

<br>
<br>
<hr color="#000000">

#### LGA
```{r, warning=F,message=F}
LGA1=linedf %>% 
  filter(ORIGIN=="LGA")
```

```{r, warning=F,message=F}
col.1 <- adjustcolor("orange red", alpha=0.4)
col.2 <- adjustcolor("blue", alpha=0.9)
edge.pal <- colorRampPalette(c(col.1, col.2), alpha = TRUE)
edge.col <- edge.pal(50)

map("state", fill=T, col="grey8", bg="grey15")

for (i in (1:dim(LGA1)[1])) { 
  inter=gcIntermediate(c(LGA1$LONGITUDE.x[1], LGA1$LATITUDE.x[1]), c(LGA1$LONGITUDE.y[i], LGA1$LATITUDE.y[i]), n=100)
  edge.ind <-(LGA1[i,]$dep_delay_)
  range(edge.ind)
  lines(inter, lwd=edge.ind/30, col=edge.col[edge.ind])
  legend("bottomleft", # position
  legend = colbm, 
  title = "Delayed length",
  fill = edge.pal(5),
  cex = 0.56,
  bty = "n") # border
}
```

<br>
<br>
<hr color="#000000">

#### EWR
```{r, warning=F,message=F}
EWR1=linedf %>% 
  filter(ORIGIN=="EWR")
```

```{r, warning=F,message=F}
col.1 <- adjustcolor("orange red", alpha=0.4)
col.2 <- adjustcolor("blue", alpha=0.9)
edge.pal <- colorRampPalette(c(col.1, col.2), alpha = TRUE)
edge.col <- edge.pal(50)

map("state", fill=T, col="grey8", bg="grey15")

for (i in (1:dim(LGA1)[1])) { 
  inter=gcIntermediate(c(EWR1$LONGITUDE.x[1], EWR1$LATITUDE.x[1]), c(EWR1$LONGITUDE.y[i], EWR1$LATITUDE.y[i]), n=100)
  edge.ind <-(EWR1[i,]$dep_delay_)
  range(edge.ind)
  lines(inter, lwd=edge.ind/30, col=edge.col[edge.ind])
  legend("bottomleft", # position
  legend = colbm, 
  title = "Delayed length",
  fill = edge.pal(5),
  cex = 0.56,
  bty = "n") # border
}
```

<br>
<br>
<hr color="#000000">

#### BOS
```{r, warning=F,message=F}
BOS1=linedf %>% 
  filter(ORIGIN=="BOS")
```

```{r, warning=F,message=F}
col.1 <- adjustcolor("orange red", alpha=0.4)
col.2 <- adjustcolor("blue", alpha=0.9)
edge.pal <- colorRampPalette(c(col.1, col.2), alpha = TRUE)
edge.col <- edge.pal(50)

map("state", fill=T, col="grey8", bg="grey15")

for (i in (1:dim(LGA1)[1])) { 
  inter=gcIntermediate(c(BOS1$LONGITUDE.x[1], BOS1$LATITUDE.x[1]), c(BOS1$LONGITUDE.y[i], BOS1$LATITUDE.y[i]), n=100)
  edge.ind <-(BOS1[i,]$dep_delay_)
  range(edge.ind)
  lines(inter, lwd=edge.ind/30, col=edge.col[edge.ind])
  legend("bottomleft", # position
  legend = colbm, 
  title = "Delayed length",
  fill = edge.pal(5),
  cex = 0.56,
  bty = "n") # border
}
```

<br>
<br>
<hr color="#000000">

#### DTW
```{r, warning=F,message=F}
DTW1=linedf %>% 
  filter(ORIGIN=="DTW")
```

```{r, warning=F,message=F}
col.1 <- adjustcolor("orange red", alpha=0.4)
col.2 <- adjustcolor("blue", alpha=0.9)
edge.pal <- colorRampPalette(c(col.1, col.2), alpha = TRUE)
edge.col <- edge.pal(50)

map("state", fill=T, col="grey8", bg="grey15")

for (i in (1:dim(DTW1)[1])) { 
  inter=gcIntermediate(c(DTW1$LONGITUDE.x[1], DTW1$LATITUDE.x[1]), c(DTW1$LONGITUDE.y[i], DTW1$LATITUDE.y[i]), n=100)
  edge.ind <-(DTW1[i,]$dep_delay_)
  range(edge.ind)
  lines(inter, lwd=edge.ind/30, col=edge.col[edge.ind])
  legend("bottomleft", # position
  legend = colbm, 
  title = "Delayed length",
  fill = edge.pal(5),
  cex = 0.56,
  bty = "n") # border
}
```

<br>
<br>
<hr color="#000000">

#### ATL
```{r, warning=F,message=F}
ATL1=linedf %>% 
  filter(ORIGIN=="ATL")
```

```{r, warning=F,message=F}

col.1 <- adjustcolor("orange red", alpha=0.4)
col.2 <- adjustcolor("blue", alpha=1)
edge.pal <- colorRampPalette(c(col.1, col.2), alpha = TRUE)
edge.col <- edge.pal(50)

map("state", fill=T, col="grey8", bg="grey15")

for (i in (1:dim(ATL1)[1])) { 
  inter=gcIntermediate(c(ATL1$LONGITUDE.x[1], ATL1$LATITUDE.x[1]), c(ATL1$LONGITUDE.y[i], ATL1$LATITUDE.y[i]), n=100)
  edge.ind <-(ATL1[i,]$dep_delay_)
  range(edge.ind)
  lines(inter, lwd=edge.ind/30, col=edge.col[edge.ind])
  legend("bottomleft", # position
  legend = colbm, 
  title = "Delayed length",
  fill = edge.pal(5),
  cex = 0.56,
  bty = "n") # border
}

```

<br>
<br>
<hr color="#000000">

#### ORD
```{r, warning=F,message=F}
ORD1=linedf %>% 
  filter(ORIGIN=="ORD")
```

```{r, warning=F,message=F}
col.1 <- adjustcolor("orange red", alpha=0.4)
col.2 <- adjustcolor("blue", alpha=1)
edge.pal <- colorRampPalette(c(col.1, col.2), alpha = TRUE)
edge.col <- edge.pal(50)

map("state", fill=T, col="grey8", bg="grey15")

for (i in (1:dim(ORD1)[1])) { 
  inter=gcIntermediate(c(ORD1$LONGITUDE.x[1], ORD1$LATITUDE.x[1]), c(ORD1$LONGITUDE.y[i], ORD1$LATITUDE.y[i]), n=100)
  edge.ind <-(ORD1[i,]$dep_delay_)
  range(edge.ind)
  lines(inter, lwd=edge.ind/30, col=edge.col[edge.ind])
  legend("bottomleft", # position
  legend = colbm, 
  title = "Delayed length",
  fill = edge.pal(5),
  cex = 0.56,
  bty = "n") # border
}
```

<br>
<br>
<hr color="#000000">

#### LAX
```{r, warning=F,message=F}
LAX1=linedf %>% 
  filter(ORIGIN=="LAX")
```

```{r, warning=F,message=F}
col.1 <- adjustcolor("orange red", alpha=0.4)
col.2 <- adjustcolor("blue", alpha=1)
edge.pal <- colorRampPalette(c(col.1, col.2), alpha = TRUE)
edge.col <- edge.pal(50)

map("state", fill=T, col="grey8", bg="grey15")

for (i in (1:dim(LAX1)[1])) { 
  inter=gcIntermediate(c(LAX1$LONGITUDE.x[1], LAX1$LATITUDE.x[1]), c(LAX1$LONGITUDE.y[i], LAX1$LATITUDE.y[i]), n=100)
  edge.ind <-(LAX1[i,]$dep_delay_)
  range(edge.ind)
  lines(inter, lwd=edge.ind/30, col=edge.col[edge.ind])
  legend("bottomleft", # position
  legend = colbm, 
  title = "Delayed length",
  fill = edge.pal(5),
  cex = 0.56,
  bty = "n") # border
}
```

<br>
<br>

<hr color="#000000">

# Conclusions

* For United States, there are more airports located in coast area than inland area. And these coast airports suffered more of the delay. Perhaps the unstable the weather near the see caused that. 

* It's very hard to find the correlation between passenger traffic and delay time, the Pearson correlation for all US airport is nearly equal to zero. But for the top 50 busiest airport, the Pearson correlation is -0.2, negative correlation between two factor, indicates an imbalance between capacity and demand. 

* From the flight path visualization, the delay for each  schedule flight is more affected by the destination location rather than the average delay of that airport. For example, JFK airport, regardless of the departure location, the departure delay for those flights  are always greater than 25mintues. What caused this phenomenon is worth further research.  


<br>
<br>

<hr color="#000000">

# References

M. Hansen (2002),"Micro-level analysis of airport delay externalities using deterministic
queuing models: a case study", Journal of Air Transport Management 8 (2002) 73–87

Antony D. Evans (2002), "RAPID MODELLING OF AIRPORT DELAY", 12th Air Transport Research Society (ATRS)
World Conference


FlightStats, Inc, Airline On-Time Performance Reports, Global Hub Departure Performance
